Automatic Repulsive Clustering \\for Finding Separable Linear Subspace

### 2016-11-28 docs/draft.tex
added multithreading

\begin{algorithm}[H]
 initialization\;
 \While{Expected likelihood $\bb E \log L$ change $>$ threshold}{
  Using $\hat \Z \hat \bmu$, compute expectation: $\bb E \V$ and $\bb E \V\V'$\;
  Using expected values, maximize: $\hat \X$ \;
   \While{change in $\hat \bmu$ $>$ threshold}{
   		  Compute MLEs: $\hat \bmu$ and $\hat \bSigma$\;
		  Compute Most Probable Assignment: $\hat \Z$ \;
	}
 Compute expected likelihood $\bb E \log L$\;
 }
 \caption{Estimation Algorithm for Automatic Repulsive Clustering}
 \label{arc_algo}
\end{algorithm}

>>>>

\begin{algorithm}[H]
 initialization\;
 \While{Change in expected likelihood $\Delta \bb E \log L$ $>$ threshold}{
  Using $\hat \Z \hat \bmu$, compute expectation: $\bb E \V$ and $\bb E \V\V'$\;
  Using expected values, maximize: $\hat \X$ \;
   \While{change in estimated $\Delta \hat \bmu$ $>$ threshold}{
   		  Compute MLEs: $\hat \bmu$ and $\hat \bSigma$\;
		  Compute Most Probable Assignment: $\hat \Z$ \;
	}
 Compute expected likelihood $\bb E \log L$\;
 }
 \caption{Estimation Algorithm for Automatic Repulsive Clustering}
 \label{arc_algo}
\end{algorithm}
